Draft Visualizations for Semester Project

### 2018-12-06 Visualizations/Draft Visualizations Template.Rmd
Added colors to two of my charts. Revised slides.

```{r}
t0 <- ggplot(health, aes(x = health$Is.your.anonymity.protected.if.you.choose.to.take.advantage.of.mental.health.or.substance.abuse.treatment.resources.provided.by.your.employer.))+geom_bar()+facet_wrap(~health$CompanySize, scales="free_y") + ggtitle("Perceived Difficulty of Asking for Leave by Gender") + xlab("Perceived Difficulty Level") + ylab("Count")+ theme(axis.title=element_text(size=12))
t0
```

@@

```{r}
#Create Visualization
t1 <- ggplot(health, aes(x = health$Is.your.anonymity.protected.if.you.choose.to.take.advantage.of.mental.health.or.substance.abuse.treatment.resources.provided.by.your.employer.))+geom_bar()+facet_wrap(health$TLabel ~ ., scales="free_y") + ggtitle("Anonymity Protections for Tech\nvs.Non-Tech Companies") + xlab("Is your anonymity protected?") + ylab("Count") + theme(axis.title=element_text(size=12))
t1
```

>>>>

```{r}
t0 <- ggplot(health, aes(x = health$Is.your.anonymity.protected.if.you.choose.to.take.advantage.of.mental.health.or.substance.abuse.treatment.resources.provided.by.your.employer.))+geom_bar(fill="purple")+facet_wrap(~health$CompanySize, scales="free_y") + ggtitle("Anonymity Protections by Comapny Size") + xlab("Perceived Difficulty Level") + ylab("Count")+ theme(axis.title=element_text(size=12))
t0
```

@@

```{r}
#Create Visualization
t1 <- ggplot(health, aes(x = health$Is.your.anonymity.protected.if.you.choose.to.take.advantage.of.mental.health.or.substance.abuse.treatment.resources.provided.by.your.employer.))+geom_bar(fill="blue")+facet_wrap(health$TLabel ~ ., scales="free_y") + ggtitle("Anonymity Protections for Tech\nvs.Non-Tech Companies") + xlab("Is your anonymity protected?") + ylab("Count") + theme(axis.title=element_text(size=12))
t1
```
